% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zihui Zheng}

\basicInfo{
  \email{echo333cheng@gmail.com} \textperiodcentered\ 
  % \phone{(+86) 131-615-72521} \textperiodcentered\ 
  \linkedin[zihuizheng]{https://www.linkedin.com/in/zihui-z-9739a582/}}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Zuora} Beijing, China}{2021-09 -- Present}
\role{Java Software Engineer, Scrum Master}{}
% Responsibilities of Sr Software Engineer
% Contribute insight to teams working to solve business problems
% Motivated to manage multiple priorities in a fast paced environment
% Ability to work as a part of a team and lead collaborative discussions in a group
% Responsibilities of Scrum Master
% Anticipate problems and establish methods to mitigate project/program risks
% Work with product owners and management to define and prioritize technology-related outcomes
% Identifies and may remove roadblocks to technology-related product development or architecture

Collaborate closely with software engineers, product owners, and architects through analysis of requirements, application/data flows, and by following the software development life cycle. Led a scrum team of size 13.
\begin{itemize}
  \item Actively engage with project teams and assist with understanding of technical solutions in Billing - Revenue integration.
  \item Provide dependable work estimates on development work and meet delivery commitments.
  \item Adjust quickly to changing priorities, requirements, and scopes during the software development life cycle.
\end{itemize}

\datedsubsection{\textbf{App Annie/data.ai} Beijing, China}{2019-05 -- 2021-09}
\role{Web Backend Engineer}{}
Worked on all phases of software development lifecycle including design, development, testing, and production support.
\begin{itemize}
  \item Developed and maintained backend APIs for App Annie Pulse, a mobile app that provides critical information about trends, markets, and apps competition in real-time.
  \item Migrated and optimized key user info aggregation API/microservice, making it 5 times faster and greatly improved user experience.
\end{itemize}

\datedsubsection{\textbf{Pocoweb} Beijing, China}{2018-08 -- 2019-03}
\role{Data Engineer, Scrum Master}{}
\begin{itemize}
  \item Provided support and troubleshooting of prior developed technology solutions and recommended effective refactoring when needed. 
  % Improved runtime of key products - customer journey and ads intelligence - to >10 times faster
  % , by refactoring code, refining data pipeline, and choosing appropriate data storage. 
  \item Dedicated to continuous process improvement through feedback loops, mentoring, retrospectives, and individual improvement.
\end{itemize}


\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Pennsylvania}, Philadelphia, USA}{2015 -- 2017}
\textit{Master of Science in Education}
\datedsubsection{\textbf{Macao Polytechnic University}, Macao, China}{2011 -- 2015}
\textit{Bachelor of Arts}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java, Python, Scheme
  \item Data Storage: PostgreSQL, MongoDB, MySQL, Redis, ClickHouse, Elastic Search
  \item AWS services: EC2, DynamoDB, Redshift, S3, Lambda, MQ, etc.
  \item Workflow: Agile methodologies, Git, Linux, Jenkins CI/CD, Jira
  \item Development: Spring, Django, Flask, RESTful API, API Gateway, microservice development
  \item Others: Knowledge in Business Intelligence, Customer Journey, Applied Data Science.
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Personalities: Enthusiastic with a positive professional attribute along with flexibility, integrity, reliability and leadership skills
  % \item GitHub: https://github.com/echocho
  \item Languages: IELTS 7.5, Cantonese, Mandarin, Japanese
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
